---
title: "How to Use This RStudio Add-in"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to Use This RStudio Add-in}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(hashpipe)
```

Install this package with `remotes::install_github("smach/hashpipe, build_vignettes = TRUE")`. It will install the package and add an RStudio add-in called hashpipe to your RStudio. All the add-in does is type '#| ' (without the quotes) at your current cursor position.

To assign this to a keyboard shortcut, go to Choose Tools > Modify Keyboard Shortcuts in RStudio. Search for the hashpipe add-in, click next to the name, type in the keyboard shortcut you want, and press Apply. 

Want to write your own RStudio add-in? Check out my _InfoWorld_ tutorial ["Do more with R: Write your own RStudio addins"](https://www.infoworld.com/article/3336059/do-more-with-r-write-your-own-rstudio-addins.html).
